Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-13 paper.qmd
Added intro to application section

XXX WHY THESE EXAMPLES. NEEDS AN OVERVIEW PARAGRAPH

>>>>

<!-- XXX WHY THESE EXAMPLES. NEEDS AN OVERVIEW PARAGRAPH -->

To showcase the robustness of our method when applied to data with different characteristics, this section presents two case studies. The first application focuses on single-cell data, a domain where the high dimensionality, sparsity, and heterogeneity of gene expression measurements pose significant analytical challenges. Our approach facilitates the identification of the most accurate NLDR layout, enabling the discovery of cell populations with similar expression profiles. The second case study explores the MNIST hand-written digits dataset, which serves as a benchmark for evaluating the preservation of local structures, specifically within a selected digit.
